Paper \#ZW10157

### 2019-01-30 paper/submission/ZW10157-response-1.tex
small grammer edits to response

{\bf Our Response:} {\color{blue} This optimization was used for design of 
an experiment. There is not an alternative base line, i.e. this is the 
``first such solution for the AWA''. They points have not been operationally measured yet.
The following line was added to the abstract:

"Optimized solutions found by the framework were used to finish the design 
of a two beam acceleration experiment."
}

@@

{\bf Our response: } {\color{blue} This section has been shortened. However we would like to 
leave the existing description, in order to drive home the fact that the framework can be 
easily extended with other optimization algorithms. Something that you can not find in most of the 
existing codes.}

@@

{\bf Our response:} {\color{blue} The code examples in sections VI-V has been removed from the updated manuscript. 
	A sentence and link to the repository have been provided. Interested parties can refer to the repository.}

>>>>

{\bf Our Response:} {\color{blue} This optimization was used for design of 
an experiment. There is not an alternative base line, i.e. this is the 
``first such solution for the AWA''. The points have not been operationally measured yet.
The following line was added to the abstract to address this:

``Optimized solutions found by the framework were used to finish the design 
of a two beam acceleration experiment.''
}

@@

{\bf Our response: } {\color{blue} This section has been shortened. However we would like to 
leave the existing description, in order to drive home the fact that the framework can be 
easily extended with other optimization algorithms.}

@@

{\bf Our response:} {\color{blue} The code examples in sections VI-V have been removed from the updated manuscript. 
	A sentence and link to the repository have been provided. Interested parties can refer to the repository.}
